---
title: "Project Title"
author: "W. Cools"
date-modified: "last-modified"
format:
  typst:
    logo-path: "_hdr_logo.png"
    email: "wilfried.cools@vub.be"
    website: "square.research.vub.be"
    template-partials:
      - typst-show.typ
      - typst-template.typ
params:
  mypar: "w's parameter in the YAML"
execute:
  echo: FALSE
  message: FALSE
  warning: FALSE
---

<!-- Project Title <project label> -->

```{r}
#| label: identification
#| echo: false
prjct <- 'client_name'
```

```{r}
#| label: if_qmd_to_r
#| eval: false
knitr::purl(paste0(prjct,".qmd"), output = paste0(prjct,".r"))
source(paste0(prjct,".r"))
# system(paste0('quarto render ',prjct,'.qmd'))
```

<!-- RUN:: libraries -->
```{r}
#| label: p_funs_intermediate
#| echo: false
pckgs <- c('tidyverse')
donotshow <- purrr::map(pckgs, library, character.only=TRUE)
```

<!-- RUN:: data -->
```{r}
#| label: data_read_rename
#| eval: false
mppng <- tribble(~output,~input,
"new1","old1",
"new2","old2")
dta <- dta %>% rename(!!! setNames(mppng$input, mppng$output))

# renaming <- c(new1="old1", new2="old2")
# dta <- dta |> rename_with(~names(renaming),all_of(as.character(renaming)))
```


> ! Current draft describes work in progress and its content should be treated as such. The researcher should remain skeptical to ensure the analyses are appropriate. 

> running `{r} R.version.string`

<!--
::: {.callout-note title='Goal'}
:::

::: {.callout-tip title='Conclusion'}
:::
-->

## Data

This template can be used for SQUARE drafts.  
The _xtra folder contains the square logo and css files for formatting.  

## Analysis

```{r}
glimpse(mtcars)
```

## Conclusion

To reach a second page, a few tables are generated.

```{r}
table(mtcars |> select(vs,cyl))
```

```{r}
head(mtcars)
```

```{r}
summary(lm(mpg~cyl,data=mtcars))
```

<!-- end of the line -->

```{r}
#| label: save_all
save.image(paste0('Γ_image_',strftime(Sys.time(), format = "%y-%m-%d"),'.RData'))
```
 